---
title: "Measurement of Policy Outcomes Homework "
author: "Alex Vaval"
date: "11/14/2020"
output: pdf_document
---

# Analyzing the French Labor Force

## (a)

The Labor Force Participation rate (LFPR) as defined by the International Organization Labour  (ILO) is the share of people the working age population  either employed or unemployed.

$$LFPR=\frac{Labour force}{Working age Population}$$
The Unemployment rate in the sense of the International Labour Office (ILO) is the number of unemployed persons in the sense of the ILO as a proportion of the labour force in the sense of the ILO.

$$U=\frac{\sum_{i=1}^{n} Unemployed_i}{\sum_{i=1}^{n}Unemployed_i*+\sum_{i=1}^{n}Employed_i}$$


## (b)

```{r,include=F}
library(haven)
library(kableExtra)
library(knitr)
library(tidyverse)
library(broom)
library(stargazer)
library(descr)

a<-read_dta("Data/lfshwk_fr11.dta")
b<-read_dta("Data/lfshwk_fr12.dta")
```

```{r,include=F}

#EMPLOYEMENT

#for 2011
# using the INSEE definition we find the variables for:
#- did a paid work during reference week
#- did a paid work for a relative's business
#- People on holiday
#-People on maternity leave
#- people having a part time job
#-people getting training paid by employer
#- people on technical unemployement
#- on strike

#filtering out for specific cases in which people
#are considered unemployed although they meet the
#conditions to be away from work.

#this is the case for people that are:
#- was not working due to sickness but less than 1 year
# - on parental leave for less than 91 days
#-  Unpaid leave less than 91 days

a<-a %>% mutate(Employed=
ifelse(( traref==1 & !is.na( traref==1))|
(aidref==1 &  tafref==2 & !is.na( aidref==1 &  tafref==2))|
(rabs==1 & !is.na(rabs==1))|
(rabs==3 & !is.na(rabs==3))|
(rabs==4 & !is.na(rabs==4))|
(rabs==7 & !is.na(rabs==7))|
(rabs==8 & !is.na(rabs==8))|
(rabs==10 & !is.na(rabs==10))|
( rabs==2 & rabsp<=365 & !is.na( rabs==2 &  rabsp<=365))|
( rabs==5 & rabsp<=91 & !is.na( rabs==5 &  rabsp<=91))|
( rabs==6 & rabsp<=91 & !is.na( rabs==6 &  rabsp<=91))|
(temp==1 & !is.na(temp==1))
,1, 0))

#for whole pop
empl_11.pop<-weighted.mean(a$Employed,a$weight,na.rm = T)
empl_1<- lm(a$Employed~1, weight=a$weight)
# for working Pop which is the real rate we want

a.rp<-a%>% filter(ag<65)
#empl_11<-weighted.mean(a.rp$Employed,a.rp$weight,na.rm = T)

empl_11<-lm(a$Employed[a$ag<65]~1,weight=a$weight[a$ag<65]) 



#for 2012
#same thing
b<-b %>% mutate(Employed=
ifelse(( traref==1 & !is.na( traref==1))|
(aidref==1 &  tafref==2 & !is.na( aidref==1 &  tafref==2))|
(rabs==1 & !is.na(rabs==1))|
(rabs==3 & !is.na(rabs==3))|
(rabs==4 & !is.na(rabs==4))|
(rabs==7 & !is.na(rabs==7))|
(rabs==8 & !is.na(rabs==8))|
(rabs==10 & !is.na(rabs==10))|
( rabs==2 & rabsp<=365 & !is.na( rabs==2 &  rabsp<=365))|
( rabs==5 & rabsp<=91 & !is.na( rabs==5 &  rabsp<=91))|
( rabs==6 & rabsp<=91 & !is.na( rabs==6 &  rabsp<=91))|
(temp==1 & !is.na(temp==1))
,1, 0))

#for whole pop
empl_12.pop<-weighted.mean(b$Employed,b$weight,na.rm = T)

# for working Pop which is the real rate we want

b.rp<-b%>% filter(ag<65)
#empl_12<-weighted.mean(b.rp$Employed,b.rp$weight,na.rm = T)
empl_12 <- lm(b$Employed[b$ag<65]~1, weight=b$weight[b$ag<65]) 
```



```{r,include=F}
#Unemployement
#3 conditions (no work, available for
#work and looking for work)

#we filter out data such that
# we find people meeting these
# 3 conditions.

#we also filter people that meet these
#conditions in the data but are clearly
#not employed
#for ex: people that have a job at moment
#of interview but have been layed off

# for 2011
a.rp<-a.rp  %>% 
mutate(Unemployed=ifelse(
(traref==2 &!is.na( traref==2) &  dispoc==1 & 
!is.na( dispoc==1) &  dem==1 & 
!is.na( dem==1) &  pastra==2 & !is.na( pastra==2))|
(traref==2 & !is.na( traref==2) & 
  dispoc==1 & !is.na( dispoc==1) & 
  dem==1 & !is.na( dem==1) &  pastra==1 &
   !is.na( pastra==1) & ( rabs==9 & !is.na( rabs==9)| 
  rabs==11 & !is.na( rabs==11)))|
( traref==2 & !is.na( traref==2) & 
dem==1 & !is.na( dem==1) & 
  dispoc==2 & !is.na( dispoc==2) &
  nondic==6 & !is.na( nondic==6))|
( tafref==2 & !is.na( traref==2) & 
    dem==1 & !is.na( dem==1) &  pastrb==1 &
!is.na( pastrb==1) &  ultj<=91 & !is.na( ultj<=91)), 1, 0))

#For 2012
b.rp<-b.rp  %>% mutate(Unemployed=ifelse(
(traref==2 &!is.na( traref==2) &  dispoc==1 & 
!is.na( dispoc==1) &  dem==1 & 
!is.na( dem==1) &  pastra==2 & !is.na( pastra==2))|
(traref==2 & !is.na( traref==2) & 
  dispoc==1 & !is.na( dispoc==1) & 
  dem==1 & !is.na( dem==1) &  pastra==1 &
   !is.na( pastra==1) & ( rabs==9 & !is.na( rabs==9)| 
  rabs==11 & !is.na( rabs==11)))|
( traref==2 & !is.na( traref==2) & 
dem==1 & !is.na( dem==1) & 
  dispoc==2 & !is.na( dispoc==2) &
  nondic==6 & !is.na( nondic==6))|
( tafref==2 & !is.na( traref==2) & 
    dem==1 & !is.na( dem==1) &  pastrb==1 &
!is.na( pastrb==1) &  ultj<=91 & !is.na( ultj<=91)), 1, 0))


U.11<-weighted.mean(a.rp$Unemployed[(a.rp$Employed==1|
  a.rp$Unemployed==1)],
  a.rp$weight[(a.rp$Employed==1|
  a.rp$Unemployed==1)],na.rm = T)

U.12<-weighted.mean(b.rp$Unemployed[(b.rp$Employed==1|
  b.rp$Unemployed==1)],
  b.rp$weight[(b.rp$Employed==1|
  b.rp$Unemployed==1)],na.rm = T)

U.11_1 <- lm(a.rp$Unemployed[a.rp$ag<65 & (a.rp$Employed==1|a.rp$Unemployed==1)]~1, weight=a.rp$weight[a.rp$ag<65 & (a.rp$Employed==1|a.rp$Unemployed==1)])
U.12_1 <- lm(b.rp$Unemployed[b.rp$ag<65 & (b.rp$Employed==1|b.rp$Unemployed==1)]~1, weight=b.rp$weight[b.rp$ag<65 & (b.rp$Employed==1|b.rp$Unemployed==1)])

E.Q1<- lm(Employed[ag<65 ]~1, weight=weight[ag<65 ],data=a.rp) 

```
\begin{table}[H] \centering 
  \caption{Unemployment and Employment Rates} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 

\\[-1.8ex] & (2011) & (2012)\\ 
\hline \\[-1.8ex] 
 Employment Rate & 0.643 & 0.643 \\ 
  & (0.001) & (0.001) \\ 
  & & \\ 
\hline \\[-1.8ex] 
Observations & 325,248 & 321,794 \\ 

\hline \\[-1.8ex] 
 Unemployment rate & 0.090 & 0.096 \\ 
  & (0.001) & (0.001) \\ 
  & & \\ 
\hline \\[-1.8ex] 
Observations & 224,207 & 223,603 \\ 
\hline 
\hline \\[-1.8ex] 

\end{tabular} 
\end{table}

For this problem set, we've considered the working age population to be the people older than younger than 65.
For the employment rate based our computation on the ILO's definition of employment which is "the people of working age who, during a short reference period, were engaged in any activity to produce goods or provide services for pay or profit."

The Employment  dummy variable was computed by looking for people that meet the following conditions of:

- Had a paid work during a reference week (traref=2)
- Had a paid work for a relative's business (aidref=1)
- Had a job but that went on holiday (rabs=1)
- Being on  maternity/paternity leave for less 91 days or less (rabs=3 & rabsp<=91)
- Had a part time job(rabs=4)
- Were getting training paid by employer (rabs=8)
- Were on sick leave for 1 year and less (rabs=2 & rabsp<=91)
- Were on unpaid leave for 91 days or less (rabs=6 & rabsp<=91)
- Were on strike (rabs=10)


The employement rate was computed by $E=\frac{\sum_{i=1}^{n} {Employed_i*Weight_i}}{\sum_{i=1}^{n} Employed_i*Weight_i+\sum_{i=1}^{n}Unemployed_i*Weight_i+\sum_{i=1}^{n}Inactive_i*Weight_i}$, for the people of the  Working age population, people from 15 to 64.


The INSEE defines an unemployed person as being someone of working age that is without employement, available to take a job within two weeks and having looked for a job in the previous month or starting one within the next three months.

The unemployment rate is calculated by expressing the number of unemployed persons as a percentage of the total number of persons in the labour force.


The Unemployment dummy variable was computed by looking for people that met the following conditions at the same time :

- People that dont have a job  (traref=2)
- Available to take a job(dispoc=1) 
- Actively looking for a job within the next 2 weeks or people starting work within 3 months (dem=1)

We had to make adjustments however because we noticed that it was possible for people  to meet all three criterias and still be logically employed for example,people that are on holiday, looking for a job, and have the possibility to leave their jobs quickly. Also the people that have a job but have been layed off (rabs=9) are not counted as unemployed while they should be.


The formula for the unemployement rate is $U=\frac{\sum_{i=1}^{n} Unemployed_i*weight_i}{\sum_{i=1}^{n}Unemployed_i*weight_i+\sum_{i=1}^{n}Employed_i*weight_i}$ which gives us share of the labour force that does not have a job.

Let us notice how the denominator is different for both variables.


## (c)
Several mentionable limitations of the unemployment rate:

- Discouraged worker

The way an unemployed person is defined means we are not counting the discouraged workers as unemployed.
Indeed, we can imagine a person unable to find a job for a long period of time (for example 1 year) that decides to stop looking for a job in which case that person becomes inactive and no longer unemployed. However, it may be that if that person were to receive a job offer, she would gladly work. Such a person should be considered unemployed but is not.
Questions accounting for these 2 conditions (unemployed for x period and willingness to work if offered a job while inactive), would help capture these people.


- Underemployment

There might be people that are not considered unemployed because they have a stable job and dont meet the conditions to be unemployed. However, these people might not work in their field of study, for example a Public Policy and development graduate working as gym instructor because she cannot find a job. In this case that person has a job, but his skill set is not utilized to its full potential. That person is actively searching for a job in her field and would be willing to leave her current job if offered.
In that case, we believe that person should be considered unemployed.





## (d)

The standard error of the mean is the how precise is our point estimate relative to the population parameter.
$$SE_{11}=\frac{\sigma}{\sqrt{n}}=\frac{\sqrt{p(1-p)}}{\sqrt{n}}=\frac{\sqrt{0.0898*0.9102}}{\sqrt{223914}}=0.00060418 $$

$$SE_{12}=\frac{\sigma}{\sqrt{n}}=\frac{\sqrt{p(1-p)}}{\sqrt{n}}=\frac{\sqrt{0.09593*0.90407}}{\sqrt{223602}}=0.00062278$$

The standard errors are very small but the 95% level confidence intervals don't overlap meaning that, we can reject the hypothesis that the Unemployment rates are the same, also we can conclude that unemployment rate increased in a statistically signifcant way between 2011 and 2012






## (e)

```{r,include=F}
#trim
#
a.rp<-a.rp%>% mutate(inactive=ifelse(Employed==0 & Unemployed==0,1,0)) %>% mutate(active=ifelse(inactive==1,0,1))
b.rp<-b.rp %>% mutate(inactive=ifelse(Employed==0 & Unemployed==0,1,0)) %>% mutate(active=ifelse(inactive==1,0,1))


#Q1
 U_Q1 <-lm(  Unemployed[ ag<65  &  trim==1]~1, weight= weight[ ag<65  &  trim==1],data=a.rp)
 
 E.Q1<- lm(Employed[ag<65 & trim==1]~1, weight=weight[ag<65 & trim==1],data=a.rp) 
 
 I.Q1 <- lm( inactive[ ag<65 &  trim==1]~1, weight= weight[ ag<65 &  trim==1],data=a.rp)

 #Q2
U_Q2 <- lm(  Unemployed[ ag<65 &   trim==2]~1, weight= weight[ ag<65  &  trim==2],data=a.rp)

E.Q2<- lm(Employed[ag<65 & trim==2]~1, weight=weight[ag<65 & trim==2],data=a.rp) 

 I.Q2<- lm( inactive[ ag<65 &  trim==2]~1, weight= weight[ ag<65 &  trim==2],data=a.rp)

#Q3
U_Q3 <- lm(  Unemployed[ ag<65 & trim==3]~1, weight= weight[ ag<65  &  trim==3],data=a.rp)

E.Q3<- lm(Employed[ag<65 & trim==3]~1, weight=weight[ag<65 & trim==3],data=a.rp) 

 I.Q3 <- lm( inactive[ ag<65 &  trim==3]~1, weight= weight[ ag<65 &  trim==3],data=a.rp)



#Q1.12

 U_Q1.12 <-lm(  Unemployed[ ag<65 &  trim==1]~1, weight= weight[ ag<65  &  trim==1],data=b.rp)
 E.Q1.12<- lm(Employed[ag<65 & trim==1]~1, weight=weight[ag<65 & trim==1],data=b.rp) 
 
  I.Q1.12 <- lm( inactive[ ag<65 &  trim==1]~1, weight= weight[ ag<65 &  trim==1],data=b.rp)
 
 #Q2.12
 
  U_Q2.12 <-lm(  Unemployed[ ag<65  &  trim==2]~1, weight= weight[ ag<65  &  trim==2],data=b.rp)
E.Q2.12<- lm(Employed[ag<65 & trim==2]~1, weight=weight[ag<65 & trim==2],data=b.rp) 

 I.Q2.12 <- lm( inactive[ ag<65 &  trim==2]~1, weight= weight[ ag<65 &  trim==2],data=b.rp)

 
 
```
\begin{table}[H] \centering 
  \caption{Evolution of the structure of the working age population} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{3}{c}{\textit{2011}}&
 \multicolumn{2}{c}{\textit{2012}} \\ 
\cline{2-6} 
\\ 
\\[-1.8ex] & Quarter 1 & Quarter 2 & Quarter 3 & Quarter 1 & Quarter 2\\ 
\hline \\[-1.8ex] 
 Employment Rate & 0.642  & 0.646  & 0.646  & 0.642  & 0.646  \\ 
  & (0.002) & (0.002) & (0.002) & (0.002) & (0.002) \\ 
  & & & & & \\ 
\hline \\[-1.8ex] 
Observations & 80,971 & 81,300 & 79,733 & 79,354 & 80,945 \\ 
 \\ 
\hline 
\hline \\[-1.8ex] 
 Unemployment Share & 0.066 & 0.060 & 0.061  & 0.069  & 0.065  \\ 
  & (0.001) & (0.001) & (0.001) & (0.001) & (0.001) \\ 
  & & & & & \\ 
\hline \\[-1.8ex] 
Observations & 80,898 & 81,188 & 79,665 & 79,272 & 80,855 \\ 
\hline 
\hline \\[-1.8ex] 

 Inactive Share & 0.292  & 0.293  & 0.292  & 0.289  & 0.289 \\ 
  & (0.002) & (0.002) & (0.002) & (0.002) & (0.002) \\ 
  & & & & & \\ 
\hline \\[-1.8ex] 
Observations & 80,915 & 81,220 & 79,686 & 79,293 & 80,881 \\

\hline 
\hline \\[-1.8ex] 

\end{tabular} 
\begin{scriptsize}
				\begin{minipage}{13cm}
				\tiny Notes: The unemployment share is different from the unemployment rate because it is the unemployed over the working age population.\newline
			\newline
			\end{minipage}
		\end{scriptsize} 

\end{table} 



```{r,include=F}
#first we drop observations! and second we cannot use weights here!!
#different weights for different quarter
#build new identifier
a.rp_e <- a.rp %>%
  mutate(noi_c = as.character(noi)) %>%
  mutate(ID = paste(ident, noi_c)) %>%
  select(Unemployed, inactive, ID, trim, Employed) %>%
  group_by(ID) %>%
  filter(trim ==1 |trim == 2 |trim == 3) %>%
  filter(length(trim) >= 3) %>%
  mutate(Unemployed_2 = ifelse(is.na(Unemployed), 0, Unemployed)) %>%
  mutate( stat = ifelse(Unemployed_2 ==1, 1, ifelse(Employed ==1,2,
                              0))) 

b.rp_e <-b.rp %>%
  mutate(noi_c = as.character(noi)) %>%
  mutate(ID = paste(ident, noi_c)) %>%
  select(Unemployed, inactive, ID, trim, Employed) %>%
  group_by(ID) %>%
  filter(trim ==1 |trim == 2) %>%
  filter(length(trim) >= 2) %>%
  mutate(Unemployed_2 = ifelse(is.na(Unemployed), 0, Unemployed)) %>%
  mutate( stat = ifelse(Unemployed_2 ==1, 1, ifelse(Employed ==1,2,
                              0))) 

#subset by quarter
a.q1 <- a.rp_e %>%
  filter(trim ==1) %>%
  select( stat11q1 =  stat, ID)

a.q2<- a.rp_e %>%
  filter(trim ==2) %>%
  select( stat11q2 = stat, ID)

a.q3 <- a.rp_e %>%
  filter(trim ==3) %>%
  select( stat11q3= stat, ID)

b.q1 <- b.rp_e %>%
  filter(trim ==1) %>%
  select( stat12q1 =  stat, ID)

b.q2 <- b.rp_e %>%
  filter(trim ==2) %>%
  select( stat12q2 =  stat, ID)


CrossTable(a.q1$stat11q1, a.q2$stat11q2)
CrossTable(a.q2$stat11q2, a.q3$stat11q3)
CrossTable(b.q1$stat12q1, b.q2$stat12q2)

```

\begin{table}[H] \centering 
  \caption{Contingent Table of labor market status between Quarters} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc}
\\\hline  
\multicolumn{2}{c}{Status in Period}  & \multicolumn{1}{c}{$2011_{Q1,Q2}$} & \multicolumn{1}{c}{$2011_{Q2,Q3}$} & \multicolumn{1}{c}{$2012_{Q1,Q2}$}\\
\cline{1-2}
t  & t+1  & \% & \% & \% \\
\hline \\[-1.8ex] 
Inactive & Inactive  & 93.5 &  91.2 &  92.8        \\
  & Unemployed  & 2.9 & 3.3 & 3.6        \\
  & Employed & 3.6 & 5.6 & 3.6        \\
  & & & &   \\ 
  \hline
  & Observations & 14,440 & 14,375 & 18,677\\ 
 \hline 
 \hline
  & & & &   \\ 
Unemployed & Inactive & 15.1 & 17.7 & 16.6  \\
& Unemployed   & 64.5 & 62.2 & 64   \\
& Employed & 20.4 & 20.1 & 19.4  \\
& & & &   \\ 
 \hline
  & Observations & 2,774 & 2,542 & 3,913\\ 
 \hline
 \hline 
Employed & Inactive  & 1.6 & 2.3 & 1.6        \\
& Unemployed   & 1.1 & 1.5 & 1.2        \\
& Employed  & 97.3 & 96.2 & 97.2   \\ 
& & & &   \\ 
 \hline
  & Observations & 29,139 & 29,436 & 38,294\\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\begin{scriptsize}
				\begin{minipage}{15cm}
				\tiny Notes: The observations are for the Quarter t not t+1.\newline
				It is read as follows; 93.5 \% of People that were inactive in the first quarter of 2011 stayed inactive in the second\newline quarter of 2011.
		
			\end{minipage}
		\end{scriptsize} 
\end{table}



We computed the Employment rate and Unemployment rate and compared them and saw that there is no statistical difference between the rates between quarters.
Therefore, we decided to compare the evolution of each individual's status between quarters as well as the globale evolution between quarters.

Quarter 1 vs Quarter 2:

The employment rate increased slightly by 0.4 percentage point, that increase is however not statistically significant, as the confidence interval overlap.
When it comes to the unemployment share (which is different than the unemployment rate), we see that there is a slight decrease in the unemployment share by 0.6 percentage point.
Lastly there seems to be a not a statistically significant increase in the inactive share between the two quarters.

Quarter 2 vs Quarter 3:

The employment rate remained constant.
When it comes to the unemployment share there seems to be a slight increase but it is not statistically significant.
Lastly, the inactive rates remains constant.

Quarter 1 vs Quarter 2 2012:

The employment rate increased slightly by 0.4 percentage point, that increase is however not statistically significant, as the confidence interval overlap.
When it comes to the unemployment share, we see that there is a sharp from 6% to 7%.
The inactive share seems to remain constant.

Overall let us notice in the Contingent table how, labour market status reproduction is the lowest for the Unemployed for all periods. What this means it that people who are unemployed can hope to not stay unemployed forever and either become employed (which is hopeful) or inactive.







## (f)
```{r,include=F}
#sexe
#age
#ddipl

b.rp<-b.rp %>% mutate(inactive=ifelse(Employed==0 & Unemployed==0,1,0)) %>% mutate(active=ifelse(inactive==1,0,1))
 U_m <-lm(  Unemployed[ ag<65 & (  Employed==1|  Unemployed==1) &  sexe==1]~1, weight= weight[ ag<65 & (  Employed==1|  Unemployed==1) &  sexe==1],data=b.rp)
U_f <- lm(  Unemployed[ ag<65 & (  Employed==1|  Unemployed==1) &  sexe==2]~1, weight= weight[ ag<65 & (  Employed==1|  Unemployed==1) &  sexe==2],data=b.rp)


### Age

U_y<-lm(Unemployed[ ag<26 & (Employed==1|Unemployed==1)]~1, weight=weight[ ag<26 &( Employed==1|Unemployed==1)],data=b.rp)
U_a <- lm(  Unemployed[ ag<55 &  ag>25 & (  Employed==1|  Unemployed==1)]~1, weight= weight[ ag<55 &  ag>25 & (  Employed==1|  Unemployed==1) ],data=b.rp)
U_o<- lm(  Unemployed[ ag<65 &  ag>54 & (  Employed==1|  Unemployed==1)]~1, weight= weight[ ag<65 &  ag>54 & (  Employed==1|  Unemployed==1)],data=b.rp)


### Education
#the relevant variable is ddipl

U_h <- lm(Unemployed[ ag<65 & (  Employed==1|  Unemployed==1)& (ddipl<=3)]~1, weight= weight[ ag<65 & (  Employed==1|  Unemployed==1) & (ddipl<=3)],data=b.rp)
U_mid <- lm(Unemployed[ ag<65 & ( Employed==1|Unemployed==1) &  (ddipl==4|ddipl==5)]~1, weight= weight[ ag<65 & ( Employed==1|  Unemployed==1) &(ddipl==4|ddipl==5)],data=b.rp)
 U_l <- lm(  Unemployed[ ag<65 & (  Employed==1|  Unemployed==1) &  (ddipl==6|ddipl==7)]~1, weight= weight[ ag<65 & (  Employed==1|  Unemployed==1) &  (ddipl==6| ddipl==7)],data=b.rp)

 

##########LABOR FORCE
 
### Gender

U_m.1 <- lm( active[ ag<65 &  sexe==1]~1, weight= weight[ ag<65 &  sexe==1],data=b.rp)
U_f.1 <- lm( active[ ag<65 &  sexe==2]~1, weight= weight[ ag<65 &  sexe==2],data=b.rp)

### Age

U_o.1 <- lm( active[ ag<65 &  ag>54 &  ddipl==1]~1, weight= weight[ ag<65 &  ag>54 &  ddipl==1],data=b.rp)
U_y.1 <- lm( active[ ag<26 &  ddipl==1]~1, weight= weight[ ag<26 &  ddipl==1],data=b.rp)
U_a.1 <- lm( active[ ag<55 &  ag>25 &  ddipl==1]~1, weight= weight[ ag<55 &  ag>25 &  ddipl==1],data=b.rp)



### Education


U_h.1 <- lm( active[ ag<65 & ddipl<=3]~1, weight= weight[ ag<65 &  ddipl<=3],data=b.rp)
U_mid.1 <- lm( active[ ag<65 &  (ddipl==4|ddipl==5)]~1, weight= weight[ ag<65 &  (ddipl==4|ddipl==5)],data=b.rp)
U_l.1 <- lm( active[ ag<65 &  (ddipl==7|ddipl==6)]~1, weight= weight[ ag<65 &  (ddipl==7|ddipl==6)],data=b.rp)



```

\begin{table}[H] \centering 
  \caption{Unemployement rate and Labor participation rate relative on socio-economic indicators} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{2}{c}{\textit{Gender}} & 
 \multicolumn{3}{c}{\textit{Age}} &  
 \multicolumn{3}{c}{\textit{Education level}}

 \\ 
\cline{2-9}  \\ 
\\[-1.8ex] & (Male) & (Female) & 15-25 & 26-54 & 55-65 & (Low) & (Average) & (High)\\ 
\hline \\[-1.8ex] 
 U & 0.095 & 0.097 & 0.220 & 0.083 & 0.070 & 0.160 & 0.095 & 0.054 \\ 
  & (0.001) & (0.001) & (0.003) & (0.001) & (0.001) & (0.002) & (0.001) & (0.001) \\ 
  & & & & & & & & \\ 
\hline \\[-1.8ex] 
N & 115,384 & 108,219 & 23,517 & 164,723 & 35,363 & 52,131 & 99,099 & 72,359 \\ 
\hline 
\hline \\[-1.8ex] 
 LFPR & 0.756 & 0.669 & 0.574 & 0.934 & 0.715 & 0.533 & 0.739 & 0.866 \\ 
  & (0.001) & (0.001) & (0.007) & (0.001) & (0.005) & (0.002) & (0.001) & (0.001) \\ 
  & & & & & & & & \\ 
\hline \\[-1.8ex] 
N & 156,338 & 165,229 & 4,449 & 34,922 & 7,480 & 100,549 & 135,835 & 84,354 \\ 
\hline 
\hline \\[-1.8ex] 

\end{tabular}
\begin{scriptsize}
				\begin{minipage}{13cm}
				\tiny Notes: U is Unemployment, N is the number of observations, LFPR is Labor Force Participation Rate. The education level scale was done looking at the distribution of the index values.  \newline
			
			\end{minipage}
		\end{scriptsize} 
\end{table}



By Gender:

In 2012, a larger share of men that were looking jobs had a job compared to females, which can partly be due to inequality in terms of job access and or gender discrimination.

Men also had a larger labor force participation than women. One possible explanation for this is that women stop working once they have kids. Another explanation is the beliefs around the role of women in society of some minorities.


By Age:

When we group the working age population by age bracket 15-25 (Young), 26-54 and 55-65(Elderly), we notice that the Youth have a higher unemployement rate than the two other groups, which makes sense because they have less experience and less qualification.The Elderly  have the lowest unemployement rate amongst the three groups,which can be explained by the fact that the people in that age bracket are likely to be in a long term stable job.

With regards to LFP, the youth has the largest share of the three groups that is inactive which makes sense considering that they're mostly getting an education.The LFPR reaches its highest in the "Adult" ages than declines again when people reach elderly age in which people start to retire.


By Education Level:

These three categories have been constructed by looking at the distribution of the index values. The values seem to be normally distributed around the mean of High school degree and CAP degree with very few people having either very high education levels (Bachelor's degree or Master's degree), and low education levels (Brevet and primary school).

First,we notice that the there is a negative correlation between education level and unemployment rate.One possible explanation for this relationship, is the fact that as one acquires more skill, it becomes progressively harder to replace him by automation.

Second, there is a positive relationship between education levels and LFPR. This can be explained by the fact that people with low education level tend to be students which are in the process of acquiring knowledge. They are therefore not participating in the Labor force because they are studying full time.


#####R CODE#####
```{r,eval=F}



library(haven)
library(kableExtra)
library(knitr)
library(tidyverse)
library(broom)
library(stargazer)
library(descr)

a<-read_dta("Data/lfshwk_fr11.dta")
b<-read_dta("Data/lfshwk_fr12.dta")


#EMPLOYEMENT

#for 2011
# using the INSEE definition we find the variables for:
#- did a paid work during reference week
#- did a paid work for a relative's business
#- People on holiday
#-People on maternity leave
#- people having a part time job
#-people getting training paid by employer
#- people on technical unemployement
#- on strike

#filtering out for specific cases in which people
#are considered unemployed although they meet the
#conditions to be away from work.

#this is the case for people that are:
#- was not working due to sickness but less than 1 year
# - on parental leave for less than 91 days
#-  Unpaid leave less than 91 days

a<-a %>% mutate(Employed=
ifelse(( traref==1 & !is.na( traref==1))|
(aidref==1 &  tafref==2 & !is.na( aidref==1 &  tafref==2))|
(rabs==1 & !is.na(rabs==1))|
(rabs==3 & !is.na(rabs==3))|
(rabs==4 & !is.na(rabs==4))|
(rabs==7 & !is.na(rabs==7))|
(rabs==8 & !is.na(rabs==8))|
(rabs==10 & !is.na(rabs==10))|
( rabs==2 & rabsp<=365 & !is.na( rabs==2 &  rabsp<=365))|
( rabs==5 & rabsp<=91 & !is.na( rabs==5 &  rabsp<=91))|
( rabs==6 & rabsp<=91 & !is.na( rabs==6 &  rabsp<=91))|
(temp==1 & !is.na(temp==1))
,1, 0))

#for whole pop
empl_11.pop<-weighted.mean(a$Employed,a$weight,na.rm = T)
empl_1<- lm(a$Employed~1, weight=a$weight)
# for working Pop which is the real rate we want

a.rp<-a%>% filter(ag<65)
#empl_11<-weighted.mean(a.rp$Employed,a.rp$weight,na.rm = T)

empl_11<-lm(a$Employed[a$ag<65]~1,weight=a$weight[a$ag<65]) 



#for 2012
#same thing
b<-b %>% mutate(Employed=
ifelse(( traref==1 & !is.na( traref==1))|
(aidref==1 &  tafref==2 & !is.na( aidref==1 &  tafref==2))|
(rabs==1 & !is.na(rabs==1))|
(rabs==3 & !is.na(rabs==3))|
(rabs==4 & !is.na(rabs==4))|
(rabs==7 & !is.na(rabs==7))|
(rabs==8 & !is.na(rabs==8))|
(rabs==10 & !is.na(rabs==10))|
( rabs==2 & rabsp<=365 & !is.na( rabs==2 &  rabsp<=365))|
( rabs==5 & rabsp<=91 & !is.na( rabs==5 &  rabsp<=91))|
( rabs==6 & rabsp<=91 & !is.na( rabs==6 &  rabsp<=91))|
(temp==1 & !is.na(temp==1))
,1, 0))

#for whole pop
empl_12.pop<-weighted.mean(b$Employed,b$weight,na.rm = T)

# for working Pop which is the real rate we want

b.rp<-b%>% filter(ag<65)
#empl_12<-weighted.mean(b.rp$Employed,b.rp$weight,na.rm = T)
empl_12 <- lm(b$Employed[b$ag<65]~1, weight=b$weight[b$ag<65]) 

#trim
#
a.rp<-a.rp%>% mutate(inactive=ifelse(Employed==0 & Unemployed==0,1,0)) %>% mutate(active=ifelse(inactive==1,0,1))
b.rp<-b.rp %>% mutate(inactive=ifelse(Employed==0 & Unemployed==0,1,0)) %>% mutate(active=ifelse(inactive==1,0,1))


#Q1
 U_Q1 <-lm(  Unemployed[ ag<65  &  trim==1]~1, weight= weight[ ag<65  &  trim==1],data=a.rp)
 
 E.Q1<- lm(Employed[ag<65 & trim==1]~1, weight=weight[ag<65 & trim==1],data=a.rp) 
 
 I.Q1 <- lm( inactive[ ag<65 &  trim==1]~1, weight= weight[ ag<65 &  trim==1],data=a.rp)

 #Q2
U_Q2 <- lm(  Unemployed[ ag<65 &   trim==2]~1, weight= weight[ ag<65  &  trim==2],data=a.rp)

E.Q2<- lm(Employed[ag<65 & trim==2]~1, weight=weight[ag<65 & trim==2],data=a.rp) 

 I.Q2<- lm( inactive[ ag<65 &  trim==2]~1, weight= weight[ ag<65 &  trim==2],data=a.rp)

#Q3
U_Q3 <- lm(  Unemployed[ ag<65 & trim==3]~1, weight= weight[ ag<65  &  trim==3],data=a.rp)

E.Q3<- lm(Employed[ag<65 & trim==3]~1, weight=weight[ag<65 & trim==3],data=a.rp) 

 I.Q3 <- lm( inactive[ ag<65 &  trim==3]~1, weight= weight[ ag<65 &  trim==3],data=a.rp)



#Q1.12

 U_Q1.12 <-lm(  Unemployed[ ag<65 &  trim==1]~1, weight= weight[ ag<65  &  trim==1],data=b.rp)
 E.Q1.12<- lm(Employed[ag<65 & trim==1]~1, weight=weight[ag<65 & trim==1],data=b.rp) 
 
  I.Q1.12 <- lm( inactive[ ag<65 &  trim==1]~1, weight= weight[ ag<65 &  trim==1],data=b.rp)
 
 #Q2.12
 
  U_Q2.12 <-lm(  Unemployed[ ag<65  &  trim==2]~1, weight= weight[ ag<65  &  trim==2],data=b.rp)
E.Q2.12<- lm(Employed[ag<65 & trim==2]~1, weight=weight[ag<65 & trim==2],data=b.rp) 

 I.Q2.12 <- lm( inactive[ ag<65 &  trim==2]~1, weight= weight[ ag<65 &  trim==2],data=b.rp)

 

#first we drop observations! and second we cannot use weights here!!
#different weights for different quarter
#build new identifier
a.rp_e <- a.rp %>%
  mutate(noi_c = as.character(noi)) %>%
  mutate(ID = paste(ident, noi_c)) %>%
  select(Unemployed, inactive, ID, trim, Employed) %>%
  group_by(ID) %>%
  filter(trim ==1 |trim == 2 |trim == 3) %>%
  filter(length(trim) >= 3) %>%
  mutate(Unemployed_2 = ifelse(is.na(Unemployed), 0, Unemployed)) %>%
  mutate( stat = ifelse(Unemployed_2 ==1, 1, ifelse(Employed ==1,2,
                              0))) 

b.rp_e <-b.rp %>%
  mutate(noi_c = as.character(noi)) %>%
  mutate(ID = paste(ident, noi_c)) %>%
  select(Unemployed, inactive, ID, trim, Employed) %>%
  group_by(ID) %>%
  filter(trim ==1 |trim == 2) %>%
  filter(length(trim) >= 2) %>%
  mutate(Unemployed_2 = ifelse(is.na(Unemployed), 0, Unemployed)) %>%
  mutate( stat = ifelse(Unemployed_2 ==1, 1, ifelse(Employed ==1,2,
                              0))) 

#subset by quarter
a.q1 <- a.rp_e %>%
  filter(trim ==1) %>%
  select( stat11q1 =  stat, ID)

a.q2<- a.rp_e %>%
  filter(trim ==2) %>%
  select( stat11q2 = stat, ID)

a.q3 <- a.rp_e %>%
  filter(trim ==3) %>%
  select( stat11q3= stat, ID)

b.q1 <- b.rp_e %>%
  filter(trim ==1) %>%
  select( stat12q1 =  stat, ID)

b.q2 <- b.rp_e %>%
  filter(trim ==2) %>%
  select( stat12q2 =  stat, ID)


CrossTable(a.q1$stat11q1, a.q2$stat11q2)
CrossTable(a.q2$stat11q2, a.q3$stat11q3)
CrossTable(b.q1$stat12q1, b.q2$stat12q2)

```{r,include=F}
#sexe
#age
#ddipl

b.rp<-b.rp %>% mutate(inactive=ifelse(Employed==0 & Unemployed==0,1,0)) %>% mutate(active=ifelse(inactive==1,0,1))
 U_m <-lm(  Unemployed[ ag<65 & (  Employed==1|  Unemployed==1) &  sexe==1]~1, weight= weight[ ag<65 & (  Employed==1|  Unemployed==1) &  sexe==1],data=b.rp)
U_f <- lm(  Unemployed[ ag<65 & (  Employed==1|  Unemployed==1) &  sexe==2]~1, weight= weight[ ag<65 & (  Employed==1|  Unemployed==1) &  sexe==2],data=b.rp)


### Age

U_y<-lm(Unemployed[ ag<26 & (Employed==1|Unemployed==1)]~1, weight=weight[ ag<26 &( Employed==1|Unemployed==1)],data=b.rp)
U_a <- lm(  Unemployed[ ag<55 &  ag>25 & (  Employed==1|  Unemployed==1)]~1, weight= weight[ ag<55 &  ag>25 & (  Employed==1|  Unemployed==1) ],data=b.rp)
U_o<- lm(  Unemployed[ ag<65 &  ag>54 & (  Employed==1|  Unemployed==1)]~1, weight= weight[ ag<65 &  ag>54 & (  Employed==1|  Unemployed==1)],data=b.rp)


### Education
#the relevant variable is ddipl

U_h <- lm(Unemployed[ ag<65 & (  Employed==1|  Unemployed==1)& (ddipl<=3)]~1, weight= weight[ ag<65 & (  Employed==1|  Unemployed==1) & (ddipl<=3)],data=b.rp)
U_mid <- lm(Unemployed[ ag<65 & ( Employed==1|Unemployed==1) &  (ddipl==4|ddipl==5)]~1, weight= weight[ ag<65 & ( Employed==1|  Unemployed==1) &(ddipl==4|ddipl==5)],data=b.rp)
 U_l <- lm(  Unemployed[ ag<65 & (  Employed==1|  Unemployed==1) &  (ddipl==6|ddipl==7)]~1, weight= weight[ ag<65 & (  Employed==1|  Unemployed==1) &  (ddipl==6| ddipl==7)],data=b.rp)

 

##########LABOR FORCE
 
### Gender

U_m.1 <- lm( active[ ag<65 &  sexe==1]~1, weight= weight[ ag<65 &  sexe==1],data=b.rp)
U_f.1 <- lm( active[ ag<65 &  sexe==2]~1, weight= weight[ ag<65 &  sexe==2],data=b.rp)

### Age

U_o.1 <- lm( active[ ag<65 &  ag>54 &  ddipl==1]~1, weight= weight[ ag<65 &  ag>54 &  ddipl==1],data=b.rp)
U_y.1 <- lm( active[ ag<26 &  ddipl==1]~1, weight= weight[ ag<26 &  ddipl==1],data=b.rp)
U_a.1 <- lm( active[ ag<55 &  ag>25 &  ddipl==1]~1, weight= weight[ ag<55 &  ag>25 &  ddipl==1],data=b.rp)



### Education


U_h.1 <- lm( active[ ag<65 & ddipl<=3]~1, weight= weight[ ag<65 &  ddipl<=3],data=b.rp)
U_mid.1 <- lm( active[ ag<65 &  (ddipl==4|ddipl==5)]~1, weight= weight[ ag<65 &  (ddipl==4|ddipl==5)],data=b.rp)
U_l.1 <- lm( active[ ag<65 &  (ddipl==7|ddipl==6)]~1, weight= weight[ ag<65 &  (ddipl==7|ddipl==6)],data=b.rp)



```





























